### 2022-05-20 results.tex
Tiny fixes. Thesis in final mode. COMPLETE.
Absolute final formatting for final handin

\section{Full model}
The full model, utilizing irradiance data from surrounding areas achieves an average MAPE of 13.21\% on the test dataset. The maximum daily average MAPE is 138.87\% and the minimum is 2.50\%. Figure~\ref{fig:days_full} shows the average MAPE the full model achieves for the test dataset on a day-by-day basis.
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=1]{imgs/graphs/full/days_full.png}
    \caption{The recorded Mean Absolute Percentage Error (MAPE) for each day in the test dataset for the full model. 
    \label{fig:days_full}}
\end{figure}

@@

\clearpage
\section{Less forecast data}
To confirm that the full model utilizes the input data for the surrounding area, we also trained the model on only the irradiance forecast for the cell the power station is located in.
The limited model achieves an average MAPE of 15.98\% on the test dataset. The maximum daily average MAPE is 122.87\% and the minimum is 3.47\%. Figure~\ref{fig:days_less} shows the average MAPE the limited model achieved for the test dataset on a day-by-day basis.
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=1]{imgs/graphs/less/days_single.png}
    \caption{The recorded Mean Absolute Percentage Error for each day in the test dataset of the limited model. 
    \label{fig:days_less}}
\end{figure}

\newpage
\subsection{Low variance days}
The model predicts most clear days with relatively high accuracy, but even on the best days, it deviates quite a bit from the observed values, as shown in Figure~\ref{fig:less_low_a}. The model sometimes under-predicts on clear days. In Figure~\ref{fig:less_low_b} we can see an example of a day where, even though the 90\% confidence area is large, the observed irradiance is outside it.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/low/low_g_1.png}\label{fig:less_low_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/low/low_b_1.png}\label{fig:less_low_b}}\qquad
    \caption{Examples of model performance on clear days.
    \label{fig:less_low}}
\end{figure}

@@

\afterpage{%
\vspace{5cm}
\begin{figure}
    \centering
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_g_1.png}\label{fig:less_med_a}}\qquad}
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_2.png}\label{fig:less_med_b}}\qquad}
    \makebox[\textwidth][c]{\subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_1.png}\label{fig:less_med_c}}\qquad
    }
    \caption{Examples of days with some drops in irradiance.
    \label{fig:less_med}}
\end{figure}
\clearpage
}

>>>>

\section{Full model}
The full model, utilizing irradiance data from surrounding areas achieves an average MAPE of 13.21\% on the test dataset. The maximum daily average MAPE is 138.87\% and the minimum is 2.50\%. Figure~\ref{fig:days_full} shows the average MAPE the full model achieves for the test dataset on a day-by-day basis.
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.8]{imgs/graphs/full/days_full.png}
    \caption{The recorded Mean Absolute Percentage Error (MAPE) for each day in the test dataset for the full model. 
    \label{fig:days_full}}
\end{figure}

@@

\clearpage
\section{Less forecast data}
To confirm that the full model utilizes the input data for the surrounding area, we also trained the model on only the irradiance forecast for the cell the power station is located in.
The limited model achieves an average MAPE of 15.98\% on the test dataset. The maximum daily average MAPE is 122.87\% and the minimum is 3.47\%. Figure~\ref{fig:days_less} shows the average MAPE the limited model achieved for the test dataset on a day-by-day basis.
\begin{figure}[ht!]
    \centering
    \includegraphics[scale=0.8]{imgs/graphs/less/days_single.png}
    \caption{The recorded Mean Absolute Percentage Error for each day in the test dataset of the limited model. 
    \label{fig:days_less}}
\end{figure}

\subsection{Low variance days}
The model predicts most clear days with relatively high accuracy, but even on the best days, it deviates quite a bit from the observed values, as shown in Figure~\ref{fig:less_low_a}. The model sometimes under-predicts on clear days. In Figure~\ref{fig:less_low_b} we can see an example of a day where, even though the 90\% confidence area is large, the observed irradiance is outside it.
\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/low/low_g_1.png}\label{fig:less_low_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/low/low_b_1.png}\label{fig:less_low_b}}\qquad
    \caption{Examples of model performance on clear days.
    \label{fig:less_low}}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_g_1.png}\label{fig:less_med_a}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_2.png}\label{fig:less_med_b}}\qquad
    \subfloat[]{\includegraphics[scale=0.5]{imgs/graphs/less/medium/med_m_1.png}\label{fig:less_med_c}}\qquad
    \caption{Examples of days with some drops in irradiance.
    \label{fig:less_med}}
\end{figure}
